---
title       : Kaggle Mobile Ad Competition
subtitle    : 1st Cut of Analysis
author      : Abhishek Kapoor
job         : Mobile Ad Competition
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides


---

## Back-ground

> 1.Hi friends, we take this competition as an opportunity to learn R and to build an architecture around R and big data

> 2.We are using Slidify and R Markdown for reporting

> 3.This competition is hosted on Kaggle - (http://www.kaggle.com/c/avazu-ctr-prediction)

> 4.Libraries we will be using are - ff,ffbase,ffbase2,ggplot2,tidyr,lubridate 

---

## Step 1 -Loading the data


```{r}
##as we are working with multi core system, we will use parallel;process to reduce the time
##requirement is RRO
rm(list=ls())###remove all the elemnts already stored in the memory

if(require(Revobase)){
  setMKLthreads(4)
}
library(ff)
library(ffbase)
library(ffbase2)
library (lubridate)
library(tidyr)
library("ggplot2")
###df <- read.csv.ffdf(file=gzfile('./train.gz'), VERBOSE=TRUE)
###ad <- tbl_ffdf(df, src="./db_ff", name="click_ads_data",force=T)
src <- src_ffdf("C:/Users/Abhishek Kapoor/Documents/GitHub/kaggle/Ad Click predictation/data/db_ff")
print (src)
ad <- tbl(src, from="click_ads") # or equivalently tbl_ffdf(src=src, name="click_ads")
tab1<- table (ad$click)
tab2<- table (ad$click,ad$banner_pos)
tab1.1<- prop.table(tab1)*100
tab1.2<-round(tab1.1, digits = 1)

tab2.1<- prop.table(tab2,2)*100
tab2.2<-round(tab2.1, digits = 1)

```

---

## Correspondence Map Coordinates

```{r}
head(ca2$col$coord)
head(ca2$row$coord)

```

---

## Correspondence Map Plot

```{r}
plot(ca2)

```

---

## Correspondence Map for end users

> 1. Now here is the link where user can easily upload the data (brand assoication data) and correspondence map will be generated in just fraction of seconds
> 2. Now user don't have to worry of running R codes, loading data or arranging the data in particular format for SPSS run. Simply upload the data and see the results
> 3. Here is the link https://kapoorabhishek.shinyapps.io/PerceptualMap/
> 4. Happy Plotting
